---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  




```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```


## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  # Fill in the missing variable!
```

Make sure to replace `___` with the appropriate column name.  


## Exercise 10  

I think the warnings are from where the date is not simply a four digit number. Some of them have "circa" or a range of dates which may mess up the function. This is fine considering our goal is to capture the year when convenient.




## Exercise 11  


```{r ex11_skim}
skim(uoe_art)
```
there are 111 pieces of artist info missing. There are 1575 years missing




## Exercise 12
histogram of year

```{r ex12_hist}
uoe_art %>%
  ggplot(aes(year)) +
  geom_histogram(
    binwidth = 10)+
  labs(title = "Number of Pieces by Year",
       x = "Year",
       y = "Count")+
  scale_x_continuous(limits = c(1810, 2025, by = 100))+
  theme_classic()
```


### Exercise 13
the most out-of-ordinary year is 2 (i cut it out of the histogram because it ruined the x axis scale) but thats becayse it was labeled as Death Mask (2) (1964) so our function pulled the 2 rather than the 1964.

To correct this 
```{r ex13_deathmask}
uoe_art <- uoe_art %>%
  mutate(year = if_else(title == "Death Mask", 1964, year))
```

### Exercise 14
```{r ex14_artist freq}
uoe_art %>%
  count(artist, sort = TRUE)

```

The most commonly featured artist is Emma Gillies. This might be because she lived in near Edinburgh but also because her brother was a director at the college. 

### Exercise 15 

```{r ex15_"child"}
uoe_art %>%
  filter(str_detect(title, "Child")) %>%
  count()
```
I got 11 titles that have the word "Child". I also checked "child" (lowercase) but didn't find any.
